\documentclass[shadesubsections,trans,14pt,mathserif]{beamer}
\usepackage[danish]{babel}	
%\usepackage[T1]{fontenc}
%\usepackage{fourier}
% Dokumentets sprog
%\usepackage{mathtools}
%\usepackage{pxfonts}
\usepackage{eulervm}
% Class options include: notes, notesonly, handout, trans,
%                        hidesubsections, shadesubsections,
%                        inrow, blue, red, grey, brown

% Theme for beamer presentation.
%\usepackage{beamertheme} 
% Other themes include: beamerthemebars, beamerthemelined, 
%                       beamerthemetree, beamerthemetreebars  
\newcommand{\adv}{\ensuremath{\mathcal A}}
\newcommand{\F}{\ensuremath{\mathbb F}}
\newcommand{\set}[1]{\ensuremath{\left\{#1\right\}}}
\newcommand{\defeq}{\ensuremath{:=}}

\title{\LARGE{Fun facts about & examples of Zero-Knowledge proofs}}    % Enter your title between curly braces
\author{\Large{Ariel Gabizon}}                 % Enter your name between curly braces
\institute{\normalsize{Protocol Labs}}      % Enter your institute name between curly braces
\date{}                    % Enter the date or \today between curly braces
%\usefonttheme{professionalfonts}
%\usefonttheme[onlymath]{serif}
\begin{document}
\boldmath
% Creates title page of slide show using above information
\begin{frame}
  \titlepage
\end{frame}
\note{Talk for 30 minutes} % Add notes to yourself that will be displayed when
                           % typeset with the notes or notesonly class options

%\section[Outline]{}

% Creates table of scontents slide incorporating
% all \section and \subsection commands
%\begin{frame}
  %\tableofcontents
%\end{frame}

\begin{frame}
  \frametitle{The deck of cards:}   % Insert frame title between curly braces
\textbf{A full deck with red and black cards, face down.}\\
 \vspace{0.4in}
\textbf{I take out a red three of hearts.}
 \vspace{0.4in}
\textbf{How to convince you I took a red card, without showing which one}
\end{frame}
\begin{frame}
  \frametitle{Proving color to the color blind:}   % Insert frame title between curly braces
\textbf{A red and green ball, otherwise indentical}\\
 \vspace{0.4in}
\textbf{How to convince a color-blind friend they are different?.}
 \vspace{0.4in}

\end{frame}

\begin{frame}
  \frametitle{Counting leaves in a tree:}   % Insert frame title between curly braces
How to prove you can instantly count the number of leaves on a tree, without disclosing the number of leaves?
\end{frame}


\begin{frame}
  \frametitle{Visual example: Where's Waldo?}   % Insert frame title between curly braces

\end{frame}


\begin{frame}
  \frametitle{Video: the cave}   % Insert frame title between curly braces
\end{frame}


\begin{frame}
 \frametitle{3-coloring}
\end{frame}



\begin{frame}
  \frametitle{From interactive to non-interactive}
\textbf{Fiat-Shamir hueristic:} simulate challenges of the verifier by hash of messages so far
 \vspace{0.4in}
  
  
\end{frame}
\begin{frame}
  \frametitle{From interactive to non-interactive}
\textbf{Fiat-Shamir hueristic:} simulate challenges of the verifier by hash of messages so far\\
 \vspace{0.4in}
\textbf{Homomorphic encryption:} Give challenge in advance in homomorphically encoded form (Craig Gentry video)
 \vspace{0.4in}
\end{frame}

\begin{frame}
  \frametitle{ZK + bitcoin: Zero-Knowledge contingent payments \small{(by Greg Maxwell)}}
\textbf{Chicken and egg problem:} I have sudoku puzzle solution, you want to buy it - who goes first?.
 \vspace{0.4in}
\end{frame}

\begin{frame}
  \frametitle{ZK + bitcoin: Zero-Knowledge contingent payments \small{(by Greg Maxwell)}}
\textbf{Chicken and egg problem:} Alice has sudoku puzzle solution, Bob want's to buy it - who goes first?.\\
 \vspace{0.4in}
\textbf{ZKCP:} Protocol where money and solution change hands at exactly same time.
 \vspace{0.4in}
\end{frame}


\begin{frame}
  \frametitle{ZK + bitcoin: Zero-Knowledge contingent payments \small{(by Greg Maxwell)}}
\begin{enumerate}
 \item Alice chooses cryptographic key  $K$, sends $h =HASH(K)$.
 \item Alice sends encrypted solution $C=E_K(S)$ to Bob; and proves in ZK: ``C is encryption of sudoku solution under key who's hash is $h$.
  \item Bob makes bitcoin ``hash-locked-transaction'' to Alice with $h$.
 \item Alice reveals $K$ to unlock her funds.
 \item Bob can now use $K$ to decrypt solution.
\end{enumerate}

\end{frame}


\begin{frame}
  \frametitle{More on the mathy side: Schnorr's discrete log protocol}
Given $g^x$, prove you know $x$ without revealing it.
\end{frame}
\begin{frame}
  \frametitle{More on the mathy side: Schnorr's discrete log protocol}
Given $X\defeq g^x$, prove you know $x$ without revealing it.
\vspace{0.4in}
\begin{enumerate}
 \item Prover chooses random $r$, sends $R\defeq g^r$.
 \item Verifier chooses random $c$
 \item Prover sends $u\defeq x\cdot c +r$
\item Verifier checks $X\cdot R = g^u$. 
\end{enumerate}

\end{frame}



\end{document}
